---
title: "DATA 607 Week 1 Extra Credit"
author: "Sean Amato"
format: 
  revealjs: 
    chalkboard: true
  html:
    code-link: true
editor: visual
execute: 
  echo: true
---

## Import Data & Packages

For this exercise I will be using data from [this website](https://vincentarelbundock.github.io/Rdatasets/articles/data.html), the data set is for psychiatric patients hospitalized with depression.

```{r}
#| label: load data and packages
#| message: false

# I uploaded the data set to my github for convenience.
depression <- read.csv("https://raw.githubusercontent.com/samato0624/DATA607/main/Ginzberg.csv")

library(tidyverse)
library(ggthemes)
library(gt)
```

## Question

To provide some background their are three columns of interest in the data set:

-   simplicity - a measure of a patient's need to see the world in black and white

-   fatalism - a measure of a patient's belief in determinism

-   depression - a self reported rating of depression

### My question is the following:

Is there a correlation between simplicity/depression and fatalism/depression?

## Data Table

#### Here are the top four patients with the highest levels of self reported depression

```{r}
depression |>
  arrange(desc(depression)) |>
  slice_head(n = 4) |>
  select(depression, simplicity, fatalism) |>
  gt() |>
  tab_style(style = list(cell_fill("lightcyan")), locations = cells_body(columns = depression)) |>
  tab_header(title = md("**Table 1**"), subtitle = md("Top 4 patients with depression")) |>
  cols_width(everything() ~ px(250))
  
```

## Simplicity vs Depression

Based on the chart below there seems to be a weak correlation between Simplicity & Depression.

```{r}
ggplot(data = depression, aes(x = simplicity, y = depression)) + 
  geom_point()
```

## Fatalism vs Depression

Based on the chart below there seems to be a very weak correlation between Fatalism & Depression.

```{r}
ggplot(data = depression, aes(x = fatalism, y = depression)) + 
  geom_point()
```
